---
#header-includes:
#  - documentclass\{beamer\}
output:
  beamer_presentation:
    keep_tex: true
    includes:
      in_header: functions.tex
  #pdf_document:
    #
    #keep_tex: true

params:
  email: "--"
  person: "--"
  action: "--"
  insight: "--"
  user: "--"
  activities: "--"
  manager: "--"
  champion: "--"
  partners: "--"
  analyst: "--"
  data: "--"
  time: "--"
  money: "--"
  deliverable: "--"
  consumed: "--"
  impact: "--"
  spillover: "--"
---

```{r, echo=FALSE}
tiny = character(25)
small = character(50)
large = character(200)
```
```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# {.noframenumbering .t}

\setbeamercolor{block title}{bg=Users, fg=white}
\beginbl{User Focus}
    \fontsize{12}{6}\selectfont
    `r params$person` will do `r params$action` differently because of `r params$insight` insight. \newline\newline
    \fontsize{12}{6}\selectfont
    Who is your user? \newline\newline\newline
    \fontsize{8}{6}\selectfont
    `r params$user` \newline\newline\newline
    \fontsize{12}{6}\selectfont
    What user activities will change? How?\newline\newline\newline
		\fontsize{8}{6}\selectfont
    `r params$activities`
\endbl

---

# {.noframenumbering .t}

\setbeamercolor{block title}{bg=Stakeholders, fg=white}
\beginbl{Stakeholders}
    \fontsize{12}{6}\selectfont
		Project Manager?\newline\newline\newline
		  \fontsize{8}{6}\selectfont
		  `r params$manager`\newline\newline\newline
    \fontsize{12}{6}\selectfont
		Client Champion?\newline\newline\newline
		  \fontsize{8}{6}\selectfont
	  	`r params$champion`\newline\newline\newline
		\fontsize{12}{6}\selectfont
		Partners?\newline\newline\newline
		  \fontsize{8}{6}\selectfont
		  `r params$partners`\newline\newline\newline
    \fontsize{12}{6}\selectfont
		Analyst?\newline\newline\newline
		  \fontsize{8}{6}\selectfont
	  	`r params$analyst`\newline
\endbl

---

# {.noframenumbering .t}
\setbeamercolor{block title}{bg=Resources, fg=white}
\beginbl{Resources}
  \fontsize{12}{6}\selectfont
	Needed Data?\newline\newline\newline
  		\fontsize{8}{6}\selectfont
		  `r params$data`\newline\newline\newline
    \fontsize{12}{6}\selectfont
		Time?\newline\newline\newline
	    \fontsize{8}{6}\selectfont
		  `r params$time`\newline\newline\newline
    \fontsize{12}{6}\selectfont
		Money?\newline\newline\newline
  		\fontsize{8}{6}\selectfont
		  `r params$money`
\endbl

---

# {.noframenumbering .t}
\setbeamercolor{block title}{bg=Deliverables, fg=white}
\beginbl{Deliverables}
  \begincols[T, onlytextwidth]
    \begincol{0.23\linewidth}
      \fontsize{12}{6}\selectfont
			 What insight is being delivered?\newline\newline\newline
  		 \fontsize{8}{6}\selectfont
			`r params$deliverable`\newline
		\endcol
	  \begincol{0.23\linewidth}
      \fontsize{12}{6}\selectfont
			How will this insight be consumed?\newline\newline\newline
  		\fontsize{8}{6}\selectfont
			`r params$consumed`\newline
		\endcol
	  \begincol{0.23\linewidth}
      \fontsize{12}{6}\selectfont
			Measure of Impact?\newline\newline\newline\newline\newline
  		\fontsize{8}{6}\selectfont
			`r params$impact`\newline
		\endcol
		\begincol{0.23\linewidth}
      \fontsize{12}{6}\selectfont
			Spillover effect?\newline\newline\newline\newline\newline
        		\fontsize{8}{6}\selectfont
      			`r params$spillover`
		\endcol
	\endcols
\endbl
